Topological Equivariant Artist Model

### 2022-01-26 slides/main.tex
phi

\section{Equivariant Artist}
\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
              \bigm{\vert} \vartistc \circ \dfuncc_{\dsectionc} \circ \dsectionc = \dfuncc_{\gsectionc} \circ \gsectionc \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{What is \dfuncc?}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}

    \begin{block}{fiber transform equivariance}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$. The bundle morphisms 
        \begin{equation*}
            \dfuncc \in Hom(\dfiberc,\dfiberc)
        \end{equation*} 
        are the set of morphisms that also preserve fiber structure.
    \end{block}
\end{frame}

@@

>>>>

\section{Equivariant Artist}

\begin{frame}{Bundle Map \dfuncc?}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}

    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

    \begin{block}{Data Transformations}
    $\dfuncc:\dtotalc\restriction_{\dbasepointc} \rightarrow \dtotalc\restriction_{\dbasepointc} \in Hom(\dfiberc\restriction_{\dbasepointc},\dfiberc\restriction_{\dbasepointc})$ 
    \end{block} 
\end{frame}

@@

\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
              \bigm{\vert} \vartistc \circ \dfuncc_{\dsectionc} \circ \dsectionc = \dfuncc_{\gsectionc} \circ \gsectionc \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}
